Missing data: Current practice in football research and recommendations for improvement

### 2020-09-05 paper/paper.Rmd
change wording in the conclusion.

Our survey of 2019 articles on football related topics
showed that current practice of reporting missing data is poor, 
with only about one in 20 studies reported missing data. To address this issue,
we have provided recommendations for reporting and exploring missing data, to assist researchers 
during this important process in the analytical pipeline.
Research should consider these recommendations, and pay greater
attention to missing data and its influence on research results.

>>>>

Our survey of 2019 articles on football related topics
showed that current practice of reporting missing data is poor, 
with only about one in 20 studies reported missing data. 
This could suggest that this aspect of data anlaysis receives little attention. 
To address this issue and assist researchers,
we have provided recommendations for reporting and exploring missing data.
Research should consider these recommendations, and pay greater
attention to missing data and its influence on research results.
